Lucky Thirteen - A Cryptographic Analyses

### 2013-07-14 paper.tex
Abstract alpha

\begin{abstract}
\textcolor{red}{TODO: clean up the text underneath, be more elaborate, fix text from all sections.}

The attack presented by~\citeauthor{alfardan2013lucky} requires $2^{23}$ TLS connections at most to get the plaintext of one encrypted block ($16$ bytes when AES is used as a block cipher), which can be decreased with different tweaks to $2^{13}$ TLS connections per byte of a cookie.
\end{abstract}

\begin{IEEEkeywords}
Cryptography, SSL, TLS, Lucky Thirteen, Padding Oracle, Timing attacks
\end{IEEEkeywords}

@@

% SECTION IV-B
\subsection{Bomb Oracles}
\label{sec:paddingoracle:bomb}
As discussed in Section~\ref{sec:paddingoracle:padding}, the attack by~\citeauthor{vaudenay2002security}~\cite{vaudenay2002security} would only work if the TLS connections would not have been terminated at the first wrongly padded plaintext received by the Oracle. The authors of a novel attack that includes multi-session byte querying~\cite{canvel2003password} have solved this issue by the introduction of so called \textit{bomb oracles}, which explode at receiving a wrongly padded plaintext, but can still go on querying for other correct paddings. Their attack makes use of the two following requirements.
\begin{itemize}
	\item The attacker is able to re-initiate the TLS session after it terminates.
	\item The secret plaintext $P^{*}$ appears in the same position in each additional TLS connection.
\end{itemize}
Fortunately, these two requirements can be met by a multi-session attack~\cite{vaudenay2002security}. The attack works by feeding the browser of the victim with specially crafted Javascript that repeatedly connects to the Oracle using a TLS connection. With every new connection that is set-up, the cookie ($P^{*}$) is at a known location in the HTTPS stream, see Figure~\ref{fig:beast_http}\footnote{For further information about the HTTPS stream, the reader is referred to the paper explaining the BEAST attack~\cite{duong2011here}, it is considered out of scope for this paper.}. In this figure, the authors of~\cite{duong2011here} have an exemplary block size of 8 bytes. They show that by controlling some of the bytes within the HTTPS stream, the bytes that the attacker is after can be forced towards a fixed position at the starting point of a new block.  This way of attacking is called a \textit{blockwise chosen-boundary attack (BCBA)}~\cite{duong2011here}.

>>>>

\begin{abstract}
This paper describes the February 2013 attack called Lucky Thirteen on TLS 1.1 and 1.2. Different sections within this paper explain the cryptographic protocols and primitives and some of the concepts of TLS that all allow for this attack. The authors of the attack describe how to decrypt ciphertext bytes from the TLS stream between some victim and an online service, which allow for cookie stealing of the victim. Some specially crafted Javascript that can run in the browser of the victim can decrypt cookie bytes by setting up $2^{13}$ TLS connections to the online service. The online service is exploited as a padding oracle, revealing information about the plaintext by validating padding encrypted in the ciphertext.

For now, the Lucky Thirteen attack is highly theoretical, but this allows for more advanced attacks that actually practically steal cookies by running within a victims browser incorporating the improvements described for this attack. The author of this paper hopes that by additional publications on the fundamental problems involved with TLS, the online community will start embracing the Authenticated Encryption introduced in TLS 1.2, which should fix all of these fundamental problems.
\end{abstract}
\begin{IEEEkeywords}
Cryptography, TLS, Lucky Thirteen, Padding Oracle, Timing attacks, BEAST, multi-session TLS attacks
\end{IEEEkeywords}

@@

% SECTION IV-B
\subsection{Bomb Oracles}
\label{sec:paddingoracle:bomb}
As discussed in Section~\ref{sec:paddingoracle:padding}, the attack by~\citeauthor{vaudenay2002security}~\cite{vaudenay2002security} would only work if the TLS connections would not have been terminated at the first wrongly padded plaintext received by the Oracle. The authors of a novel attack that includes multi-session byte querying~\cite{canvel2003password} have solved this issue by the introduction of so called \textit{bomb oracles}, which explode at receiving a wrongly padded plaintext, but can still go on querying for other correct paddings. Their attack makes use of the two following requirements.
\begin{itemize}
	\item The attacker is able to re-initiate the TLS session after it terminates.
	\item The secret plaintext $P^{*}$ appears in the same position in each additional TLS connection.
\end{itemize}
Fortunately, these two requirements can be met by a multi-session attack~\cite{vaudenay2002security}. The attack works by feeding the browser of the victim with specially crafted Javascript that repeatedly connects to the Oracle using a TLS connection. With every new connection that is set-up, the cookie ($P^{*}$)\footnote{For simplicity reasons, cookies are seen as a block of $16$ bytes in the paper. In fact, they can have a variable length.} is at a known location in the HTTPS stream, see Figure~\ref{fig:beast_http}\footnote{For further information about the HTTPS stream, the reader is referred to the paper explaining the BEAST attack~\cite{duong2011here}, it is considered out of scope for this paper.}. In this figure, the authors of~\cite{duong2011here} have an exemplary block size of 8 bytes. They show that by controlling some of the bytes within the HTTPS stream, the bytes that the attacker is after can be forced towards a fixed position at the starting point of a new block.  This way of attacking is called a \textit{blockwise chosen-boundary attack (BCBA)}~\cite{duong2011here}.
